---
title: "A real world example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A real world example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is practically the same code you can find on this blog post of mine:
https://www.brodrigues.co/blog/2018-11-14-luxairport/
but with some minor updates to reflect the current state of the `{tidyverse}` packages as well
as logging using `{loud}`.

```{r setup}
library(loud)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)

data("avia")

# Define required functions

l_select <- loudly(select)
l_pivot_longer <- loudly(pivot_longer)
l_filter <- loudly(filter)
l_mutate <- loudly(mutate)
l_separate <- loudly(separate)
l_group_by <- loudly(group_by)
l_summarise <- loudly(summarise)

```

```{r}
avia_clean <- avia %>%
  l_select(1, contains("20")) %>% # select the first column and every column starting with 10
  bind_loudly(l_pivot_longer, -starts_with("unit"), names_to = "date", values_to = "passengers") %>%
  bind_loudly(l_separate,
              col = 1,
              into = c("unit", "tra_meas", "air_pr\\time"),
              sep = ",") 

```

Let’s focus on monthly data:

```{r}
avia_monthly <- avia_clean %>%
  bind_loudly(l_filter,
              tra_meas == "PAS_BRD_ARR",
              !is.na(passengers),
              str_detect(date, "M")) %>%
  bind_loudly(l_mutate,
              date = paste0(date, "01"),
              date = ymd(date)) %>%
  bind_loudly(l_select,
              destination = "air_pr\\time", date, passengers)

```

`avia_monthly` is an object of class `loud`, but in essence, it is just a list, with its own
print method:

```{r}
avia_monthly
```

Now that the data is clean, we can take a look at the log and see what was done:

```{r}

avia_monthly %>%
  pick("log_df")

```

This is especially useful if the object `avia_monthly` gets saved using `saveRDS()`. People that
then read this object, can read the log to know what happened and reproduce the steps if necessary.

Let's take a look at the final data set:

```{r}
avia_monthly %>%
  pick("result")
```

It is also possible to see how look the computation took:

```{r}
avia_monthly %>%
  pick("log_df") %>%
  summarise(total_run_time = sum(run_time))

```
